Exponential Integrals\\ [1ex]

### 2022-02-11 draft2.tex
Fix sign error in y-x factor
Continue counterclockwise in 3/2-derivative check
Now we get w_+, as expected, instead of w_-.

\begin{claim}\label{claim 2}
\begin{equation}
\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds \qquad \zeta\in(2/3,+\infty)
\end{equation}
\end{claim}

@@

&= 2\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\
&= -\frac{2}{9} \int_{2/3}^{\zeta}(\zeta-s)^{-1/2} \left[ {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}-\frac{3s}{4}\right) - {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}+\frac{3s}{4}\right) \right] ds & 15.8.28 \text{ DLMF} \\
&=\frac{4}{9\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-y\right)\right]dy & x\in (-\infty,0) \\
&=\frac{4}{9\sqrt{3}} \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(5/3) \pi i} y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right. \\

@@

Continue $w_5$ and $w_6$ clockwise around their singularities at zero.}

@@

&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{|y|^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right. \\
& \qquad\qquad\qquad\qquad\qquad\qquad \left. + e^{-(2/3) \pi i} \frac{|y|^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\

@@

&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \left[ e^{-(1/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{3})} \frac{|x|^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right. \\
& \qquad\qquad\qquad\qquad \left. + e^{-(2/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3})} \frac{|x|^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right] & \eqref{4.8} \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{-(1/3) \pi i} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} e^{-(7/6) \pi i} x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) \right. \\
& \left. \qquad\qquad\qquad\qquad + e^{-(2/3) \pi i} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} e^{-(11/6) \pi i} x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right) \right] \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{-(1/3) \pi i} e^{-(7/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(2) \Gamma(\tfrac{1}{6})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right. \\
& \qquad\qquad\qquad\qquad + \left. e^{-(2/3) \pi i} e^{-(11/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(2) \Gamma(\tfrac{5}{6})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{-(2/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(1/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\Gamma(\tfrac{3}{2})\,\Gamma(\tfrac{1}{2})}{\tfrac{4}{3}\Gamma(\tfrac{4}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} \frac{\tfrac{1}{6}\Gamma(\tfrac{1}{6})\,\tfrac{5}{6}\Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{-(1/2) \pi i} e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right. \\
& \qquad\qquad\qquad\qquad\qquad\qquad\qquad + \left. e^{(1/2) \pi i} e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\,\tfrac{1}{2}\Gamma(\tfrac{1}{2})\,\Gamma(\tfrac{1}{2})}{\tfrac{4}{3}\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} \frac{5}{6^2} (-i) \left[ e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) - e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\,\tfrac{1}{2}}{\tfrac{4}{3}\,\tfrac{1}{3}\,\tfrac{2}{3}} \frac{5}{6^2} \frac{\sin(\tfrac{1}{3}\pi)}{\sin(\tfrac{1}{2}\pi)} (-i) \left[e^{(7/6) \pi i} - e^{(11/6) \pi i}\right]\,w_3(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
&=\frac{5 \cdot 3\pi}{12^2} \frac{\sqrt{3}}{2} i\sqrt{3}\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;1-x\right) \\
&=\frac{5\pi i}{32} \,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}+\frac{3\zeta}{4}\right) \\

@@

This matches the LHS of claim~\eqref{claim 2} \textbf{(up to scaling)}, as long as we continue from above the branch cut. This is consistent \textbf{(is it?)} with our continuations of $w_5$ and $w_6$ \textbf{(name)} in the calculation.

>>>>

\begin{claim}\label{claim 2}
\textbf{[There should be a way to predict the correct normalization of the LHS.]}
\begin{equation}
\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds \qquad \zeta\in(2/3,+\infty)
\end{equation}
\end{claim}

@@

&= 2\int_{2/3}^{\zeta} (\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\
&= -\frac{2}{9} \int_{2/3}^{\zeta} (\zeta-s)^{-1/2} \left[ {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}-\frac{3s}{4}\right) - {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}+\frac{3s}{4}\right) \right] ds & 15.8.28 \text{ DLMF} \\
&=\frac{4}{9\sqrt{3}}\int_0^x (y-x)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-y\right)\right]dy & x\in (-\infty,0) \\
&=\frac{4}{9\sqrt{3}} \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \int_0^x (y-x)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(5/3) \pi i} y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right. \\

@@

Continue $w_5$ and $w_6$ counterclockwise around their singularities at zero.} Notice that $|y - x| = y - x$ on the integration path.

@@

&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x |y-x|^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(10/3) \pi i} |y|^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right. \\
& \qquad\qquad\qquad\qquad\qquad\qquad \left. + e^{-(2/3) \pi i} \frac{e^{(14/3) \pi i} |y|^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x |y-x|^{-1/2}\left[ -\frac{|y|^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right. \\
& \qquad\qquad\qquad\qquad\qquad\qquad \left. + \frac{|y|^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\

@@

&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \left[ -\frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{3})} \frac{|x|^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right. \\
& \qquad\qquad\qquad\qquad \left. + \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3})} \frac{|x|^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right] & \eqref{4.8} \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} e^{(7/6) \pi i} x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) \right. \\
& \left. \qquad\qquad\qquad\qquad + \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} e^{(11/6) \pi i} x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right) \right] \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(2) \Gamma(\tfrac{2}{3})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right. \\
& \qquad\qquad\qquad\qquad + \left. \frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(2) \Gamma(-\tfrac{2}{3})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{1}{\Gamma(\tfrac{2}{3}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right. \\
& \qquad\qquad\qquad\qquad + \left. \frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{1}{\Gamma(-\tfrac{2}{3}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{\sin(\tfrac{2}{3} \pi)}{\pi} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right. \\
& \qquad\qquad\qquad\qquad + \left. \frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{\sin(-\tfrac{2}{3} \pi)}{\pi} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
&=\frac{8\pi}{27} \frac{\sqrt{3}}{2\pi} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) - \frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right]

@@

Using DLMF~15.10.25, we see this is
&=-\frac{8}{27} \frac{\sqrt{3}}{2} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
&=-\frac{8}{27} \frac{\sqrt{3}}{2} \frac{\tfrac{3}{2}\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{1}{2})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\,\tfrac{5}{6}\Gamma(\tfrac{5}{6})}{\tfrac{4}{3}\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
&=-\frac{5\sqrt{3}}{6 \cdot 2^4} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{1}{2})\,\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{1}{3})\Gamma(\tfrac{2}{3})} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
&=-\frac{5\sqrt{3}}{6 \cdot 2^4} \frac{\pi \sin(\tfrac{1}{3}\pi)}{\sin(\tfrac{1}{6}\pi)} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
&=-\frac{5\pi}{32} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
&=-\frac{5\pi}{32}\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;x\right) \\
&=-\frac{5\pi}{32}\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}-\frac{3\zeta}{4}\right) \\
&=-\frac{5\pi}{32}\hat{w}_+(\zeta - 2/3)
This matches $-\sqrt{\pi}$ times the LHS of claim~\eqref{claim 2} \textbf{(up to scaling)}.
